Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
SUBMITTABLE :)

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.6\columnwidth]{freqs}
\end{center}
\caption{\small{ Usage frequency of the patterns in the codebook from
    Figure \ref{fig:codes1} on the artist20 dataset.  There are $71,832$
    patterns in total in the dataset.  Note that all codes were
    initialized with a random sample from the training set and might
    not be used in this test set.
    FIXME: so why not show usage in training data?  I think test.mat
    should contain this information.
  }}
\label{fig:freqs}
\end{figure}

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{freqs}
\end{center}
\caption{\small{Usage frequency of the patterns in the codebook from
Figure \ref{fig:codes1} on the artist20 dataset.  There are $71,832$
patterns in total in the dataset. Also frequency on the training set.
Note that even though all codewords are initialized from sample, some
are used only once (training set) or never (test set).
}}
\label{fig:freqs}
\end{figure}
